Abstract Binding Trees

### 2015-10-24 paper.tex
Try and implement symbol/parameter renaming (resolve #10)

@@

@@

\newcommand\IsRenaming[3]{
  \IMode{#2}\upharpoonright\IMode{#1}%
  \leadsto\OMode{#3}%
}

@@

@@

Because terms are identified up to $\alpha$-equivalence, the variable
substitution judgment is functional in its inputs, and so we are justified in
writing $\Subst{N}{x}{M}$ for $M'$ when $\IsSubst{N}{x}{M}{M'}$. We write
$\Subst{\vec{N}}{\vec{x}}{M}$ for the simultaneous substitution of $\vec{N}$
for $\vec{x}$ in $M$.

>>>>

\newcommand\ArrDom[1]{\mathsf{dom}(#1)}
\newcommand\Match[2]{\IMode{#1}\equiv\OMode{#2}}

@@

\newcommand\Renaming[2]{
  #2\upharpoonright #1
}
\newcommand\IsRenaming[3]{
  \Renaming{\IMode{#1}}{\IMode{#2}}%
  \leadsto\OMode{#3}%
}

@@

@@

\subsection{Renaming of Symbols}

The only place that symbols appear in our calculus is as parameters to
operators (unlike variables, symbols are not terms). Therefore, the functorial
action of the operator presheaf can be lifted into terms by recursion on their
structure, via a pair of judgments $\IsRenaming{\varrho}{M}{N}$ and
$\IsRenaming{\varrho}{E}{F}$, presupposing
$\Of{\varrho}{\Upsilon\to\Upsilon'}$, and $\IsAbt{\Omega}{\Upsilon}{\Gamma}{M}{s}$
and $\IsAbt{\Omega}{\Upsilon}{\Gamma}{E}{v}$ respectively:

\begin{gather*}
  \infer{
    \IsRenaming{\varrho}{x}{x}
  }{
  }\\[6pt]
  \infer{
    \IsRenaming{\varrho}{
      \MApp{\MV{m}}{\vec{u}}{M_0,\dots,M_n}
    }{
      \MApp{\MV{m}}{\vec{v}}{N_0,\dots,N_n}
    }
  }{
    \Match{\varrho(\vec{u})}{\vec{v}} &
    \HypJ{
      \IsRenaming{\varrho}{M_i}{N_i}
    }{
      \Leq{i}{n}
    }
  }\\[6pt]
  \infer{
    \IsRenaming{\varrho}{
      \App{\vartheta}{E_0,\dots,E_n}
    }{
      \App{\vartheta'}{F_0,\dots,F_n}
    }
  }{
    \Match{\Restriction{\varrho}(\vartheta)}{\vartheta'} &
    \HypJ{
      \IsRenaming{\varrho}{E_i}{F_i}
    }{
      \Leq{i}{n}
    }
  }\\[6pt]
  \infer{
    \IsRenaming{\varrho}{
      \left(\MkBTm{\vec{u}}{\vec{x}}{M}\right)
    }{
      \left(\MkBTm{\vec{u}}{\vec{x}}{N}\right)
    }
  }{
    \IsRenaming{\varrho\setminus\vec{u}}{M}{N}
  }
\end{gather*}

Above, the notation $\varrho\setminus\vec{u}$ means the omission of the
variables $\vec{u}$ from the renaming $\varrho$. Because terms are identified
up to $\alpha$-equivalence, the renaming judgment is functional in its input,
and so we are justified in writing $\Renaming{\varrho}{M}$ for $N$ when
$\IsRenaming{\varrho}{M}{N}$.

@@

Going forward, we will write $\Subst{N}{x}{M}$ for $M'$ when
$\IsSubst{N}{x}{M}{M'}$, and $\Subst{\vec{N}}{\vec{x}}{M}$ for the
simultaneous substitution of $\vec{N}$ for $\vec{x}$ in $M$.
